Specialisation \& the Latitude-niche-breadth Hypothesis

### 2015-10-11 talk/ABC_2015.tex
Punched up all the figures

      \end{center}
    \column{.5in}
    \column{1.75in}
      \begin{center}
      \includegraphics[height=1in]{Figures/version1.eps}\\
      \vspace{.5cm}
      Similar specialisation\\at all latitudes

@@

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_lat_simulated.eps}

    \vspace{.5cm}
    {\color{white}... and species richness varies with latitude}
    \end{center}

@@

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_fitline_observed.eps}

    \vspace{.5cm}
    {\color{white}... and species richness varies with latitude}
    \end{center}

@@

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_fitline_observed.eps}

      \vspace{.5cm}
    ... and species richness varies with latitude
    \end{center}

  \begin{frame}{Does latitude affect G vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_fitline_observed.eps}

      \vspace{.5cm}
    \end{center}
    \hspace{1in}
      $G \approx aS^{\color{purple}b}$

  \begin{frame}{Does latitude affect G vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}

      \vspace{.5cm}
    \end{center}
    \hspace{1in}
      $G \approx aS^{\color{purple}b_0+b_1Latitude}$

  \begin{frame}{Does latitude affect G vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}

      \vspace{.5cm}
    \end{center}
    \hspace{1in}
      $G \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$

\section*{Results}
  \begin{frame}{Does latitude affect G vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_marginal_axis.eps}

@@

  \begin{frame}{Does latitude affect G vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_marginal_one.eps}

@@

  \begin{frame}{Does latitude affect G vs. S?}
    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_marginal.eps}

@@

>>>>

      \end{center}
    \column{.5in}
    \column{1.75in}
      \begin{center}
      \includegraphics[height=1in]{Figures/version2.eps}\\
      \vspace{.5cm}
      Similar specialisation\\at all latitudes

@@

    \begin{center}
      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_lat_simulated.eps}
    \end{center}

@@

    \begin{center}
      \includegraphics*[width=.654\textwidth]{Figures/results/Gen_dots_vs_S_fitline_observed.eps}

    \vspace{.3cm}
    \end{center}
      \hspace{.74cm}
      {\Large      
      $G \approx aS^{\color{purple}b}$}
  \end{frame}

  \begin{frame}{Does latitude affect scaling?}

    \begin{center}
      \includegraphics*[width=.654\textwidth]{Figures/results/Gen_dots_vs_S_fitline_observed.eps}

      \vspace{.3cm}
    \end{center}
      \hspace{.74cm}
      {\Large
      $G \approx aS^{\color{purple}b_0+b_1Latitude}$}
  \end{frame}

  \begin{frame}{Does latitude affect scaling?}
    \begin{center}
      \includegraphics*[width=.654\textwidth]{Figures/results/Gen_dots_vs_S_fitline_observed.eps}

      \vspace{.3cm}
    \end{center}
      \hspace{.74cm}
      {\Large
      $G \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$}

@@

\section*{Results}
  \begin{frame}{Does latitude affect scaling?}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/Gen_vs_S_marginal_axis.eps}

      \vspace{.8cm}
      ${\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$

@@

  \begin{frame}{Does latitude affect scaling?}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/Gen_vs_S_marginal_one.eps}

      \vspace{.8cm}
      ${\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$

@@

  \begin{frame}{Does latitude affect scaling?}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/Gen_vs_S_marginal.eps}

      \vspace{.8cm}
      ${\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$

@@

  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/no_effect.eps}

      \vspace{1cm}
      {\color{white} No effect of latitude on scaling\\
      Similar niche widths at all latitude\\
      \vspace{.54cm}        
      Supports Davies \emph{et. al.}, 2007:\\
      Broader niche space in the tropics}

  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/no_effect.eps}

      \vspace{1cm}
      No effect of latitude on scaling\\
      {\color{white}Similar niche widths at all latitude\\
      \vspace{.54cm}      
      Supports Davies \emph{et. al.}, 2007:\\
      Broader niche space in the tropics}

  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/no_effect.eps}

      \vspace{1cm}
      No effect of latitude on scaling\\
      Similar niche widths at all latitude\\
      \vspace{.54cm}
      {\color{white} Supports Davies \emph{et. al.}, 2007:\\
      Broader niche space in the tropics}

  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/no_effect.eps}

      \vspace{1cm}
      No effect of latitude on scaling\\
      Similar niche widths at all latitude\\
      \vspace{.54cm}      
      Supports Davies \emph{et. al.}, 2007:\\
      Broader niche space in the tropics

  \begin{frame}{Lake \& Stream Food Webs}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/effect_mod.eps}

      \vspace{1cm}
      {\color{white} Scaling increases with latitude\\
      Narrower niches in the tropics\\
      \vspace{.54cm}      
      Supports Vazquez \& Stevens 2004\\}
      {\color{white} narrower niches in the tropics}

  \begin{frame}{Lake \& Stream Food Webs}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/effect_mod.eps}

      \vspace{1cm}
      Scaling increases with latitude\\
      {\color{white} Narrower niches in the tropics\\
      \vspace{.54cm}      
      Supports Vazquez \& Stevens 2004\\}
      {\color{white} narrower niches in the tropics}

  \begin{frame}{Lake \& Stream Food Webs}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/effect_mod.eps}

      \vspace{1cm}
      Scaling increases with latitude\\
      Narrower niches in the tropics\\
      \vspace{.54cm}     
      {\color{white} Supports Vazquez \& Stevens 2004\\}
      {\color{white} narrower niches in the tropics}

  \begin{frame}{Lake \& Stream Food Webs}
    \begin{center}
      \includegraphics*[width=.9\textwidth]{Figures/results/effect_mod.eps}

      \vspace{1cm}
      Scaling increases with latitude\\
      Narrower niches in the tropics\\
      \vspace{.54cm}
      Supports Vazquez \& Stevens 2004\\
      {\color{white} narrower niches in the tropics}

  \begin{frame}{What's different in freshwaters?}
    Seasonality?\\
    NZ streams are weird but probably don't affect much\\
    Gape limitation?\\
  \end{frame}
